A boundary-integral framework to simulate \\ the viscous erosion of a porous medium

### 2018-04-06 docs/methods/erosion_methods.tex
NM

\paragraph{Limitations}
We make two fundamental design choices in our simulation: first, we restrict ourselves to
two spatial dimensions, and second the bodies are considered immobile
(i.e.~fixed to their initial locations). The restriction to two
dimensions allows us to simulate the erosion of many bodies (up to $50$
in this manuscript) with high resolution, giving us the ability to
accurately characterize the erosion of a porous medium. While BIEs are
available in three dimensions, the extra computational cost limits the
number of bodies that could be practically simulated, making
porous-medium simulations less feasible. The second assumption of
immobile bodies affords a simple framework to study the effects of
erosion in isolation. While other effects, such as sedimentation or
transport, undoubtedly play a role in real applications, these effects
would introduce additional complexity, both conceptually and
numerically. We therefore defer the study of these effects to future
work.

>>>>

\paragraph{Limitations}
We make two fundamental design choices in our simulation: first, we restrict attention to
two spatial dimensions, and second the bodies are considered immobile
(i.e.~fixed to their initial locations). The restriction to two
dimensions allows us to simulate the erosion of many bodies (up to $50$
in this manuscript) with high resolution, giving us the ability to
accurately characterize the erosion of a porous medium. While BIEs are
available in three dimensions, the extra computational cost limits the
number of bodies that could be practically simulated, making
porous-medium simulations less feasible. The second assumption of
immobile bodies affords a simple framework to study the effects of
erosion in isolation. While other effects, such as sedimentation or
transport, undoubtedly play a role in real applications, these effects
would introduce additional complexity, both conceptually and
numerically. We therefore defer the study of these effects to future
work.
